KidsAIR wood stove grades and usage

### 2020-10-23 main_analysis_initial.Rmd
small data cleaning updates

@@

```{r}
# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>%
  rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  distinct(area, home, .keep_all = TRUE)

@@

char_funct_total("gender_parent")
char_funct_treatment("gender_parent")
char_funct_total("hispanic_parent")
char_funct_treatment("hispanic_parent")
char_funct_total("race_parent")
char_funct_treatment("race_parent")
char_funct_total("education_3level")
char_funct_treatment("education_3level")
char_funct_total("income_3level")
char_funct_treatment("income_3level")
char_funct_total("home_floors_2level")
char_funct_treatment("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_treatment("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_treatment("home_pets_2level")
char_funct_total("home_pets")
char_funct_treatment("home_pets")
char_funct_total("stove_age_3level")
char_funct_treatment("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_treatment("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_treatment("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_treatment("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_treatment("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_treatment("burn_level_3level")
char_funct_total("ruca_code")
char_funct_treatment("ruca_code")
char_funct_total("ruca_code_2")
char_funct_treatment("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_treatment("ruca_code_3")
char_funct_total("residents_smoke")
char_funct_treatment("residents_smoke")
char_funct_total("residents_smoke_inside")
char_funct_treatment("residents_smoke_inside")
```

```{r}
# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>%
  rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  distinct(area, home, .keep_all = TRUE)

@@

at_home_pm_summary <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>%
  rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  mutate(new_var = pm_at_home_sampling_period) %>% 
  filter(!is.na(new_var)) %>%
  group_by(treatment) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
at_home_pm_summary
```

```{r}
# Initial summary data for LRTI
incidence_summary <- analysis_data %>% 
  group_by(treatment) %>% 
  #filter(lrti_incidence < 0.7) %>% 
  summarize(mean_inc = mean(lrti_incidence, na.rm = TRUE),
            sd_inc = sd(lrti_incidence, na.rm = TRUE),
            n_inc = n(),
            min_inc = min(lrti_incidence, na.rm = TRUE),
            median_inc = median(lrti_incidence, na.rm = TRUE),
            max_inc = max(lrti_incidence, na.rm = TRUE))
incidence_summary

@@

# amb data summary
# amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti
ambient_summary <- analysis_data %>% 
  mutate(new_var = amb_pm_lrti) %>% 
  #group_by(treatment) %>% 
  filter(!is.na(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  summarize(mean_amb = mean(new_var, na.rm = TRUE),
            sd_amb = sd(new_var, na.rm = TRUE),
            n_amb = n(),
            min_amb = min(new_var, na.rm = TRUE),
            median_amb = median(new_var, na.rm = TRUE),
            max_amb = max(new_var, na.rm = TRUE))
ambient_summary

>>>>

health_exposure_data_sampling_day <- 
  read_rds(paste0(file_path, "Output/health_exposure_data_sampling_day.rds")) %>% 
  mutate(home_pets = as.factor(home_pets),
         home_pets_3level = fct_collapse(home_pets,
                                    "0" = "0",
                                    "1" = "1",
                                    "2+" = c("2","3","4","5","6","7","8","9","10","12","14")))

@@

```{r}
# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>%
  rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  filter(area == "NN") %>% 
  distinct(area, home, .keep_all = TRUE)

@@

char_funct_total("gender_parent")
char_funct_treatment("gender_parent")
char_funct_total("race_parent")
char_funct_treatment("race_parent")
char_funct_total("education_3level")
char_funct_treatment("education_3level")
char_funct_total("income_3level")
char_funct_treatment("income_3level")
char_funct_total("home_floors_2level")
char_funct_treatment("home_floors_2level")
char_funct_total("home_year_built_2level")
char_funct_treatment("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_treatment("home_pets_2level")
char_funct_total("home_pets_3level")
char_funct_treatment("home_pets_3level")
char_funct_total("residents_smoke")
char_funct_treatment("residents_smoke")
char_funct_total("residents_smoke_inside")
char_funct_treatment("residents_smoke_inside")
char_funct_total("stove_age_3level")
char_funct_treatment("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_treatment("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_treatment("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_treatment("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_treatment("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_treatment("burn_level_3level")
char_funct_total("ruca_code")
char_funct_treatment("ruca_code")
char_funct_total("ruca_code_2")
char_funct_treatment("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_treatment("ruca_code_3")
```

```{r}
# clean up data for table 1 summary
table_1_data <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>%
  rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  filter(area == "NN") %>% 
  distinct(area, home, .keep_all = TRUE)

@@

at_home_pm_summary <- health_exposure_data_sampling_day %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>%
  rename(treatment = newtx) %>% 
  arrange(area, home, winter_id, sampling_day) %>% 
  filter(winter_id == 1) %>% 
  distinct(area, child_id_num, .keep_all = TRUE) %>% 
  mutate(new_var = pm_at_home_sampling_period) %>% 
  filter(!is.na(new_var)) %>%
  filter(area == "NN") %>% 
  group_by(treatment) %>% 
  summarize(mean_var = mean(new_var), sd_var = sd(new_var), n_var = n(), 
            min_var = min(new_var), med_var = median(new_var), max_var = max(new_var))
at_home_pm_summary
```

```{r}
# Initial summary data for LRTI
incidence_summary <- analysis_data %>% 
  filter(area == "NN") %>% 
  #group_by(treatment) %>% 
  #filter(lrti_incidence < 0.7) %>% 
  summarize(mean_inc = mean(lrti_incidence, na.rm = TRUE),
            sd_inc = sd(lrti_incidence, na.rm = TRUE),
            n_inc = n(),
            min_inc = min(lrti_incidence, na.rm = TRUE),
            median_inc = median(lrti_incidence, na.rm = TRUE),
            max_inc = max(lrti_incidence, na.rm = TRUE))
incidence_summary

@@

# amb data summary
# amb_pm_lrti, amb_temp_lrti, amb_dewp_lrti, amb_pressure_lrti, amb_wind_lrti
ambient_summary <- analysis_data %>% 
  filter(area == "NN") %>% 
  mutate(new_var = amb_pm_lrti) %>% 
  group_by(treatment) %>% 
  filter(!is.na(new_var)) %>% 
  #mutate(new_var = (as.numeric(new_var)-32)*5/9) %>% 
  summarize(mean_amb = mean(new_var, na.rm = TRUE),
            sd_amb = sd(new_var, na.rm = TRUE),
            n_amb = n(),
            min_amb = min(new_var, na.rm = TRUE),
            median_amb = median(new_var, na.rm = TRUE),
            max_amb = max(new_var, na.rm = TRUE))
ambient_summary

### 2020-10-23 stove_grade_usage_cleaning.Rmd
small data cleaning updates

kids_kw_clean <- kids_kw %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>%  
  filter(!is.na(home)) %>% 
  arrange(area, home_winter_id, kw_date) %>% 
  group_by(area, home_winter_id) %>% 
  mutate(kw_hours_total = sum(kw_hours))

@@

kw_summary <- kids_kw_clean %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>% 
  distinct(area, home, kw_hours_total) %>% 
  ungroup() %>% 
  #group_by(newtx) %>% 
  summarize(mean(kw_hours_total),
            sd(kw_hours_total),
            n(),
            min(kw_hours_total),
            median(kw_hours_total),
            max(kw_hours_total))
kw_summary

>>>>

kids_kw_clean <- kids_kw %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>%  
  filter(!is.na(home)) %>% 
  arrange(area, home_winter_id, kw_date) %>% 
  group_by(area, home_winter_id) %>% 
  mutate(kw_hours_last = last(kw_hours),
         diff_check = if_else(kw_hours_last < kw_hours, 1, 0),
         diff_check2 = kw_hours_last - kw_hours)  
  distinct(area, home_winter_id, diff_check, .keep_all = TRUE)

@@

kw_summary <- kids_kw_clean %>% 
  select(-treatment_assigned, -treatment_actual) %>% 
  left_join(treatments_masked, by = "home") %>% 
  distinct(area, home, kw_hours_total) %>% 
  ungroup() %>% 
  filter(area == "WMT") %>% 
  #group_by(newtx) %>% 
  summarize(mean(kw_hours_total),
            sd(kw_hours_total),
            n(),
            min(kw_hours_total),
            median(kw_hours_total),
            max(kw_hours_total))
kw_summary
